---
title: "Index Creation"
author: "C Armour"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

require(sf)
require(tidyverse)
require(pbapply)
require(future)
require(parallel)
require(arcgisbinding)
require(lidR)
require(future)
require(terra)
require(magrittr)

terra::terraOptions(overwrite = T, todisk = T, tempdir = "E:/temp")

## Write simple function to source all other functions so we can refresh with a simple function call
source_functions <- function(){
  list.files(str_c(getwd(), "/functions"), pattern = ".R$", full.names = T) %>% lapply(source)
}

source_functions()
```

At least once every six months, the index of available LiDAR files should be re-downloaded from the portal. The code chunk below will check the date of the most recent index and download a newer version if applicable and an ArcGIS license is available. It returns the file path of the relevant geopackage after this operation.

If you need to update manually for some reason, the instructions to do
this are as follows:

1.  Navigate to LidarBC Map Grid
    <https://governmentofbc.maps.arcgis.com/home/item.html?id=5f6a1f31212a4cb2826743d2e52ef02a>
2.  Select `Open in ArcGIS Desktop` -\> `Open in ArcGIS Pro`
3.   Double click `item.pitemx` file to open in ArcGIS. This is also
    stored in the `las_index_files` folder.
4.  Download point cloud index layer (eg
    `Point Cloud Index - 1:2,500 Grid`)
5.  Use "`Export Features`" tool and save to the `las_index_files`
    folder using the following format: "`las_index_YYYY-MM-DD.shp`"
6.  Read this shapefile in as your index. Optional: export as `.gpkg`.

```{r get-lidar-layers}

## Pull the AOI index
index <- make_gpkg_index() %>% st_read()

```
